Sperm should evolve to make female meiosis fair.

### 2014-12-24 writeup_and_notes/evolution/response_drive_MS.tex

You've got some nice reviewer comments here, which should definitely be addressed. In particular, reviewer 2, aka Gardner, made two suggestions that I see as critical.
\\ \\
{\bf{AE comment 1:}} First is the suggestion to consider inbreeding. Personally, I'm not sure it would be worth the effort at this point to write out and analyze a full-on model of a structured population with migration, etc, etc. It's a fantastic idea, and definitely worth doing, but maybe it's the next paper.

However, it would be easy to tweak each model with the inclusion of one or two F values, to give you excess homozygosity (or excess probability of green-beard matching). For example, in model 3, you mention this narrow region of parameter space that exists only when the paternal modifier functions similarly in sperm from heterozygous and homozygous fathers. One thing that inbreeding would do is increase the likelihood of occupying that space. Would that then make a sustained polymorphism biologically plausible? If so, what would that predict for the evolution of female meiosis in highly inbred populations?

{\bf{Response to AE comment 1:}}  \emph{We note that both R1 and R2 noted an interest in the case of inbreeding. We therefore have explored the behavior of model 2 [as well as model one for reference to the case of traditional drive] under six values of inbreeding. We briefly discuss these results in the modified text and make the figures [analogous to Figure 1B] in the Supplement.}
\\
\\
\\
{\bf{AE comment 2:}} Second is the taxonomic question. The phylogenetic distribution of post-fertilization completion of female meiosis is critical to the evolutionary implications of this work. Even if the data is spotty at the moment, it would be worth spelling out what is known. Plus, you could maybe make your phylogenetic hypotheses a bit more specific that way.

{\bf{Response to AE comment 2:}}  \emph{We have now included a phylogeny of animals showing the phylogenetic distribution of the stage of female meiosis, at which fertilization occurs. This has been left as a supplementary figure as we do not view this as key to our arguments; however, we believe it is a nice addition to the paper.  We hope that this data and our pointing to it in the main text, highlights this under appreciated biology and encourages additional research}. We thank reviewers \& editor for this suggestion. 
\\
\\
\\
{\bf{AE comment 3:}} 
A couple of comments regarding the discussion section:

### 2014-12-24 writeup_and_notes/evolution/RESUBMISSIONmale_dependent_drive.tex
yb for submission 12/24/14

It is therefore somewhat surprising that despite the intense evolutionary pressure on female meiosis to prevent meiotic drive, 
it is potentially open to sabotage by a virtual stranger -- a haploid sperm genome.
That is, in many animal species, female meiosis is completed only
after fertilization \citep{Masui_book}, creating ample opportunity for interaction between the sperm and
%	female meiotic machinery (note that the alternation of generations
%	likely precludes this interaction in plants). 
\yb{	female meiotic machinery (note that, across animals the variation in timing of sperm entry into the egg and the timing at which female meiosis stalls [supplementary Figure XXX] complicates this opportunity in some taxa, and that the alternation of generations likely precludes this interaction in plants).}
%\gc{The timing of entry of sperm into the egg relative to the
%  progression of female meiosis is variable across animals, as is the
%  stage at which female meiosis
%  stalls without fertilization (we show the phylogenetic distribution
%  in supplementary Figure XXX).}
Therefore, in many species a `green-bearded' \citep{Gardner2010} sperm-acting allele that recognizes and facilitates the meiotic drive of a genetically equivalent allele in heterozygous females could presumably rapidly spread through a population. 
At first sight, female meiosis appears primed for conflict caused by such selfish systems. 
Here we ask if sperm do indeed evolve to collaborate with female drivers to exploit this 
	apparent weakness in the defense against meiotic drive. \newline

@@

Because female meiotic drive is likely a common force with predictably negative effects on organismal fitness,  
	and because sperm have ample opportunity to influence female drive,  
	we develop population genetic models to address the the expected influence of sperm on female drive.  
We first focus on models in which `self-promoting' alleles in
  sperm facilitate drive of like alleles during gametogenesis in heterozygous females. 
These models show that such sperm-acting alleles 
	have more difficulty invading a population than do traditional meiotic drivers, 
	 and under most circumstances, cannot be maintained as a balanced polymorphism.
Because self-promoting drivers are unlikely to create a sustained genomic conflict, 
	female meiosis will have little incentive to evolve resistance to them.
We then examine models in which a novel sperm-acting allele modifies the efficacy of a polymorphic meiotic driver. 
Such models universally reveal that sperm-acting drive modifiers are favored only if they suppress drive. 
These results highlight the fact that the interests of sperm and
maternal  genomes' are often aligned, 
as both are invested in the fate of the resultant zygote \citep[as was speculated for the \emph{In} locus, ][]{Pomiankowski1993}.
Thus, there is little selective benefit to females in preventing sperm to influence female meioses, 
	and in fact, females eschewing this delay would potentially lose sperm assistance in the suppression of meiotic drivers.  
\yb{Given the wide-spread requirement of fertilization for the completion
	of  female meiosis, various features of the interaction between sperm 
	and egg may result in an equitable transfer of genetic material -- 
	wether this result is the ultimate evolutionary function of the fertilization requirement or a coincidental pleiotropic outcome is beyond the scope of this manuscript, 
	but our intuition argues against the prior (see Discussion).}

@@

We verbally describe our main results below.  
Readers interested in the details of these results should turn to the Appendix for a mathematical treatment, 
	and to our Mathematica worksheet  (File S2) for our complete derivations. 
There, we present critical analytical results in Equations 1-11, and describe our analyses and results in more detail.  
Because a number of our analyses are approximations based on assuming
that genotype frequencies follow Hardy Weinberg Equilibrium (HWE), we note which analytical results are approximate. 
We verify these approximations with exact numerical iterations in Figures S1-S3 and File S3.

@@

Inclusion of a heterozygous fitness cost (i.e. $w_{AB}=1-s_h$)
	further constrains the evolution of a self-promoting driver. 
In fact, with any heterozygous fitness cost, a rare self-promoting
	driver is always selected against. 
However, this case also displays bistability -- 
	when $s$ is sufficiently small (Equation \ref{sForHetFix}) this allele fixes deterministically if its 
	frequency exceeds some threshold  (Equation \ref{thresh2}, exact results in 
	Figure \ref{bistable_additive}).
This bistability prevents self-promoting drivers from invading 	
	reasonably sized populations, and assures that if they do invade, they will rapidly fix.
Our model therefore predicts that self-promoting drivers will not be
	observed as stable polymorphisms in natural populations. 
This lack of a balanced polymorphism %(Figure \ref{Invasion_space}) 
	precludes the evolution of an
	allele that suppresses this form of meiotic drive in females. 
\gc{ \yb{Relaxing our assumptions of panmixia by} allowing for 
  arbitrary levels of inbreeding (in the form of self-fertilization),
  %, as opposed to the panmictic model exploredabove -- 
  more thoroughly aligns the interests of both parents and
  parental chromosomes, restricting further the possibility for
  invasion of both traditional female drivers and 'self-promoting'
  drivers (Figures SXX-SXY). Additionally, because inbreeding reduces
  the frequency of heterozygotes, the invasion and fixation criteria
  converge, \yb{as both become stricter with increased inbreeding rates}.} \newline

@@

\subsection*{Major result: Sperm evolve to enforce fairness in female meiosis.} 
It seems that allowing sperm to influence the outcome of female meiosis would generate a confluence of these potential conflicts -- 
	sperm could actually assist an allele that distorts female meiosis.
However, this is not the case.
We find that an allele which acts through sperm to distort female meiosis in its favor %YB [too awkward / unclear?] 
	can rarely spread through a population if it bears any cost. 
Additionally, when this self-promoting driver can spread, it can only rarely 
	be maintained as a protected polymorphism, and due to its positive frequency dependence,  
	it spends very little time at intermediate frequency.
As such, this type of exploitation cannot generate a sustained genetic conflict.
It is therefore unlikely
	that female o\"{o}genesis and meiosis will evolve to prevent their effect.  
Thus, females can delay the completion of meiosis until after fertilization 
	without risking exploitation by collaborations between female
        drivers and sperm alleles. 
\yb{Although the fertilization requirement allows sperm an opportunity to enforce fairness in female meiosis, 
	this is unlikely it evolutionary raison d'\^{e}tre. 
In fact, to suggest so, presupposes that sperm have an evolved system, to prevent meiotic drive before they have a mechanism to do so.}
\newline 
%%G: felt like this made it sound less why they do it.

@@

\yb{The theory developed above has one overarching conclusion -- that when possible, males evolve to make female meiosis fair. 
This simple result provides numerous novel predictions, many of which are directly testable.

Our most direct prediction is that for organisms in which female  meiosis is not completed until after fertilization, 
	sperm will act to suppress female drive at the stage at which they can influence meiosis. 
This prediction, which holds when modifier and driver are the same gene (Model 2) or are in tight linkage (Model 4),  
	is strongly supported by the observation that female meiosis 
	is fairer when fertilized by sperm bearing the drive allele in 
	two of the best described cases of female meiotic drive in 
	animals \citep[the \emph{Om} and \emph{In} loci in mice, ][]{Agulnik1993,Wu2005}.  
Both this prediction, and the empirical support for it run contrary to expectations of a na\"{i}ve verbal ``green-beard'' model. 
}

\yb{Our model of a sperm-acting drive suppressor unlinked to a female driver (Model 6) also predicts that sperm should evolve to prevent meiotic drive; 
	however, it contains no simple mechanism to maintain polymorphism for sperm-acting drive suppression.
Given the benefit to sperm of hampering female drive, 
	drive-suppressing sperm are often likely to be fixed within a species, 
	making the hypothesis of sperm-acting drive-suppression difficult to test from intra-population crosses. 
However, crosses between populations or species are likely to provide critical tests of our theory -- 
	specifically we predict that female meiosis will be less fair when a species (or population) is 
	fertilized by heterospecific sperm because either such sperm have not evolved to counter novel female meiotic drivers, 
	or because antagonistic coevolution between a driver-suppressor pair has been independent since two populations have separated. 
We can therefore predict that segregation in F1 females backcrossed to parental species will likely be biased, 
	with a deficit of transmission of the paternal species allele from the F1  female.   
These predictions follow straightforwardly from the
	theory presented above; however, we caution that tests of meiotic drive, 
	and especially sperm-dependent meiotic drive require a high standard
	of evidence  to exclude plausible alternative hypotheses such as genotypic 
	inviability including epistatic maternal by zygotic lethality \citep[e.g. ][]{Sawamura:1993aa}.  \newline
}

@@

\yb{
For example, we predict that a lower opportunity for female meiotic drive,
        e.g. an animal lineage with a history of high inbreeding or selfing, 
        may be accompanied by a relaxation of the requirement of fertilization for the
        completion of female meiosis (although 
        opportunities to test this hypothesis may be limited because 
        lineages may only persist for a short time). 
This prediction follows from the logic that although the benefit of sperm protection from drivers did not necessarily favor the evolution of the fertilization requirement, 
	mutants who forge this requirement will experience a higher level of meiotic drive than individuals who do not.  
Therefore removing this requirement is safest in populations with little drive. 
We caution that other constraints on the fertilization requirement could prevent species from conforming to this prediction.
}

Our results also suggests that phylogenetic variation in the stage of female meiosis when
        fertilization occurs \gc{(see Supplementary Figure XXX)} may influence the prevalence of  female meiotic drive.
For example, centromeric drive may be more common  in taxa where females complete MI before fertilization, 
	as compared to species in which sperm interact with eggs arrested  in MI, 
	because in the prior case, sperm-based modifiers can only intercede during the second, but not the first  meiotic division. 
As a potential test of this hypothesis, the speed of centromere
	turnover could be compared in species in which sperm interact with eggs paused at MI and MII 
	(assuming the pace of centromere turnover serves as a proxy for the frequency of MI drivers). 
\newline

\section*{Conclusion}
Our results highlight potentially counterintuitive results of complex genetic conflicts. 
Despite much opportunity for conflict between sperm and females over fertilization \citep{Partridge1998},
	the interests of fertilizing sperm and female are quite well aligned during syngamy.
While conflict between mother and her alternative chromosomes ensues, 
	fertilizing sperm decidedly side with mom, as both have a shared interest in producing a viable and potentially fit offspring. 
Our model does not directly speak to the evolutionary origin of
  female meiotic arrest \citep[for a review and evaluation of such
  hypotheses see][]{Mira1998}, in fact, we presuppose its existence.
However, given the existence of female meiotic arrest, 
	and that its timing and mechanistic details are variable
        across species \citep[Supplementary Figure XXX, and][ ]{Masui_book,Karrbook:09},
	the nature of the meiotic arrest and interactions between
        sperm and egg may  be molded by selection to reduce the opportunity for female meiotic drive, 
	and counteracted by selfish drivers evolving to overcome these adaptations.

@@

\subsubsection*{Model 4. Drive-modifier in coupling phase:}
When the $C$ allele is tightly linked to the driver allele, 
	genotypic fitnesses equal $w_{AC}=w_{AB}=1-s_h$, and $w_{BC}=w_{CC}=w_{BB}=1-s$. 
Assuming HWE, a recessive fitness cost to drive, and assuming that the $A/B$ locus is at its equilibrium frequency, the change in frequency of a rare drive modifier is
\begin{equation}
	\Delta C\approx -\epsilon f_C \frac{ 1-2 d_0 (-2 d_0+s+2)+\sqrt{2} \sqrt{s (2 d_0 (d_0(s-2)+2)-1)}}{2 \bar{w}(1-2 d_0)^2}
	\label{coupling}
\end{equation}
%YB Considered this ugly math more impressive.
For all parameters sustaining a polymorphism at the drive locus ($s>d_0-1/2$), this corresponds to a decrease in frequency of the $C$ allele when it enhances drive ($\epsilon >0$ -- the $B^+$ model, above), 
	and an increase in frequency of the $C$ allele when it suppresses drive ($\epsilon <0$ -- the $B^-$ model, above). 
More generally, even when the cost of drive is not fully recessive, the $B^-$ allele will invade and fix under all parameters sustaining a previous polymorphism at the drive locus (see File S2  ).

\subsubsection*{Model 5. Drive-modifier in repulsion phase:}
When the $C$ allele is tightly linked to the non-driver, 
	genotypic fitnesses equal $w_{CC}=w_{AC}=w_{AA}=1$, and $w_{BC}=w_{AB}=1-s_h$. 
Assuming HWE, a recessive fitness cost to drive, and assuming that the $A/B$ locus is at its equilibrium frequency, the change in frequency of a rare drive modifier is
\begin{equation}
	\Delta C \approx -\epsilon f_{C^-}^2 \frac{ \left(2 d_0 s-\sqrt{2} \sqrt{s (2 d_0 (d_0 (s-2)+2)-1)}\right)}{2\bar{w}s (2 d_0 -1) }. \label{A-}
\end{equation}
For all values of interest ($0<s<1$, $0.5<d_0<1$), the change in frequency a rare $C$ allele is positive when it decreases drive (i.e. $\epsilon <0$, corresponding to the $A^-$ model, above), a result which holds qualitatively for a common $C$ allele, as well (File S2  ). 
%Somewhat counterintuitively, the spread of the $A^-$ allele is somewhat slower than that of the $B^-$ allele (it is on the order of $C^{2}$ rather than $C$). 
%This is because the $A^-$ allele will never occur in drive-homozygotes and therefore only spreads by preventing itself from the cheating of the driver.
% YB COMMENT {I removed bc this was actually quite a minor influence}

@@

{\bf{File S1:}} Transmission rules. We detail the frequency of offspring genotypes produced by each possible mating for Models 1-6 in the tabs of this Excel spreadsheet.

{\bf{Files S2A \& S2B:}} A Mathematica file (FileS2A) and a PDF of this file (File S2B) in which we derive analytical results for models 1-6 and $6^\prime$.

{\bf{File S3:}} Exact approach. The R Script used for exact recursions.
\clearpage

@@

\begin{figure}
%\includegraphics[width = \textwidth]{supp/meiotic_phylogeny.pdf}
\caption{The phylogenetic distribution of the female meiotic
  arrest. The first two columns of symbols gives the stage of the ooycte when
  the sperm penerates and the stage at which it arrests if
  unfertilized. The third column of symbols shows the site for natural fertilization. 
  These columns of phenotypic data were extracted from Table
  1 of \citet{Masui_book}. The tree was extracted from the Open Tree of
Life project. The raw data table and script to do this is included in
the supplement. }  
\label{Meiotic_fig}
\end{figure}

@@

>>>>

It is therefore somewhat surprising that despite the intense evolutionary pressure on female meiosis to prevent meiotic drive, 
it is potentially open to sabotage by a virtual stranger -- a haploid sperm genome.
That is, in many animal species, female meiosis is completed only
after fertilization \citep{Masui_book}, creating ample opportunity for interaction between the sperm and
female meiotic machinery (note that, across animals the variation in timing of sperm entry into the egg and the timing at which female meiosis stalls (Figure \ref{Meiotic_fig}) complicates this opportunity in some taxa, and that the alternation of generations likely precludes this interaction in plants).
Therefore, in many species a `green-bearded' \citep{Gardner2010} sperm-acting allele that recognizes and facilitates the meiotic drive of a genetically equivalent allele in heterozygous females could presumably rapidly spread through a population. 
At first sight, female meiosis appears primed for conflict caused by such selfish systems. 
Here we ask if sperm do indeed evolve to collaborate with female drivers to exploit this 
	apparent weakness in the defense against meiotic drive. \newline

@@

Because female meiotic drive is likely a common force with predictably negative effects on organismal fitness,  
	and because sperm have ample opportunity to influence female drive,  
	we develop population genetic models to address the the expected influence of sperm on female drive.  
We first focus on models in which `self-promoting' alleles in
  sperm facilitate drive of like alleles during gametogenesis in heterozygous females. 
These models show that such sperm-acting alleles 
	have more difficulty invading a population than do traditional meiotic drivers, 
	 and under most circumstances, cannot be maintained as a balanced polymorphism.
Because self-promoting drivers are unlikely to create a sustained genomic conflict, 
	female meiosis will have little incentive to evolve resistance to them.
We then examine models in which a novel sperm-acting allele modifies the efficacy of a polymorphic meiotic driver. 
Such models universally reveal that sperm-acting drive modifiers are favored only if they suppress drive. 
These results highlight the fact that the interests of sperm and
maternal  genomes' are often aligned, 
as both are invested in the fate of the resultant zygote \citep[as was speculated for the \emph{In} locus, ][]{Pomiankowski1993}.
Thus, there is little selective benefit to females in preventing sperm to influence female meioses, 
	and in fact, females eschewing this delay would potentially lose sperm assistance in the suppression of meiotic drivers.  
Given the wide-spread requirement of fertilization for the completion
	of  female meiosis, various features of the interaction between sperm 
	and egg may result in an equitable transfer of genetic material -- 
	wether this result is the ultimate evolutionary function of the fertilization requirement or a coincidental pleiotropic outcome is beyond the scope of this manuscript, 
	but our intuition argues against the prior (see Discussion).

@@

We verbally describe our main results below.  
Readers interested in the details of these results should turn to the Appendix for a mathematical treatment, 
	and to our Mathematica worksheet  (File S2) for our complete derivations. 
There, we present critical analytical results in Equations 1-11, and describe our analyses and results in more detail.  
Because a number of our analyses are approximations based on assuming
that genotype frequencies follow Hardy Weinberg Equilibrium (HWE), we note which analytical results are approximate. 
We verify these approximations with exact numerical iterations in Figures S2-S4 and File S3.

@@

Inclusion of a heterozygous fitness cost (i.e. $w_{AB}=1-s_h$)
	further constrains the evolution of a self-promoting driver. 
In fact, with any heterozygous fitness cost, a rare self-promoting
	driver is always selected against. 
However, this case also displays bistability -- 
	when $s$ is sufficiently small (Equation \ref{sForHetFix}) this allele fixes deterministically if its 
	frequency exceeds some threshold  (Equation \ref{thresh2}, exact results in 
	Figure \ref{bistable_additive}).
This bistability prevents self-promoting drivers from invading 	
	reasonably sized populations, and assures that if they do invade, they will rapidly fix.
Our model therefore predicts that self-promoting drivers will not be
	observed as stable polymorphisms in natural populations. 
This lack of a balanced polymorphism %(Figure \ref{Invasion_space}) 
	precludes the evolution of an
	allele that suppresses this form of meiotic drive in females. 
Relaxing our assumptions of panmixia by allowing for 
  arbitrary levels of inbreeding (in the form of self-fertilization, implemented in File S3),
  %, as opposed to the panmictic model exploredabove -- 
  more thoroughly aligns the interests of both parents and
  parental chromosomes, restricting further the possibility for
  invasion of both traditional female drivers and 'self-promoting'
  drivers (Figure \ref{self}). Additionally, because inbreeding reduces
  the frequency of heterozygotes, the invasion and fixation criteria
  converge, as both become stricter with increased inbreeding rates.\newline

@@

\subsection*{Major result: Sperm evolve to enforce fairness in female meiosis.} 
It seems that allowing sperm to influence the outcome of female meiosis would generate a confluence of these potential conflicts -- 
	sperm could actually assist an allele that distorts female meiosis.
However, this is not the case.
We find that an allele which acts through sperm to distort female meiosis in its favor %YB [too awkward / unclear?] 
	can rarely spread through a population if it bears any cost. 
Additionally, when this self-promoting driver can spread, it can only rarely 
	be maintained as a protected polymorphism, and due to its positive frequency dependence,  
	it spends very little time at intermediate frequency.
As such, this type of exploitation cannot generate a sustained genetic conflict.
It is therefore unlikely
	that female o\"{o}genesis and meiosis will evolve to prevent their effect.  
Thus, females can delay the completion of meiosis until after fertilization 
	without risking exploitation by collaborations between female
        drivers and sperm alleles. 
Although the fertilization requirement allows sperm an opportunity to enforce fairness in female meiosis, 
	this is unlikely it evolutionary raison d'\^{e}tre. 
In fact, to suggest so, presupposes that sperm have an evolved system, to prevent meiotic drive before they have a mechanism to do so.
\newline 
%%G: felt like this made it sound less why they do it.

@@

The theory developed above has one overarching conclusion -- that when possible, males evolve to make female meiosis fair. 
This simple result provides numerous novel predictions, many of which are directly testable.

Our most direct prediction is that for organisms in which female  meiosis is not completed until after fertilization, 
	sperm will act to suppress female drive at the stage at which they can influence meiosis. 
This prediction, which holds when modifier and driver are the same gene (Model 2) or are in tight linkage (Model 4),  
	is strongly supported by the observation that female meiosis 
	is fairer when fertilized by sperm bearing the drive allele in 
	two of the best described cases of female meiotic drive in 
	animals \citep[the \emph{Om} and \emph{In} loci in mice, ][]{Agulnik1993,Wu2005}.  
Both this prediction, and the empirical support for it run contrary to expectations of a na\"{i}ve verbal ``green-beard'' model.

Our model of a sperm-acting drive suppressor unlinked to a female driver (Model 6) also predicts that sperm should evolve to prevent meiotic drive; 
	however, it contains no simple mechanism to maintain polymorphism for sperm-acting drive suppression.
Given the benefit to sperm of hampering female drive, 
	drive-suppressing sperm are often likely to be fixed within a species, 
	making the hypothesis of sperm-acting drive-suppression difficult to test from intra-population crosses. 
However, crosses between populations or species are likely to provide critical tests of our theory -- 
	specifically we predict that female meiosis will be less fair when a species (or population) is 
	fertilized by heterospecific sperm because either such sperm have not evolved to counter novel female meiotic drivers, 
	or because antagonistic coevolution between a driver-suppressor pair has been independent since two populations have separated. 
We can therefore predict that segregation in F1 females backcrossed to parental species will likely be biased, 
	with a deficit of transmission of the paternal species allele from the F1  female.   
These predictions follow straightforwardly from the
	theory presented above; however, we caution that tests of meiotic drive, 
	and especially sperm-dependent meiotic drive require a high standard
	of evidence  to exclude plausible alternative hypotheses such as genotypic 
	inviability including epistatic maternal by zygotic lethality \citep[e.g. ][]{Sawamura:1993aa}.

@@

For example, we predict that a lower opportunity for female meiotic drive,
        e.g. an animal lineage with a history of high inbreeding or selfing, 
        may be accompanied by a relaxation of the requirement of fertilization for the
        completion of female meiosis (although 
        opportunities to test this hypothesis may be limited because 
        lineages may only persist for a short time). 
This prediction follows from the logic that although the benefit of sperm protection from drivers did not necessarily favor the evolution of the fertilization requirement, 
	mutants who forge this requirement will experience a higher level of meiotic drive than individuals who do not.  
Therefore removing this requirement is safest in populations with little drive. 
We caution that other constraints on the fertilization requirement could prevent species from conforming to this prediction.

Our results also suggests that phylogenetic variation in the stage of female meiosis when
        fertilization occurs (see Figure \ref{Meiotic_fig}) may influence the prevalence of  female meiotic drive.
For example, centromeric drive may be more common  in taxa where females complete MI before fertilization, 
	as compared to species in which sperm interact with eggs arrested  in MI, 
	because in the prior case, sperm-based modifiers can only intercede during the second, but not the first  meiotic division. 
As a potential test of this hypothesis, the speed of centromere
	turnover could be compared in species in which sperm interact with eggs paused at MI and MII 
	(assuming the pace of centromere turnover serves as a proxy for the frequency of MI drivers). 
\newline

\section*{Conclusion}
Our results highlight potentially counterintuitive results of complex genetic conflicts. 
Despite much opportunity for conflict between sperm and females over fertilization \citep{Partridge1998},
	the interests of fertilizing sperm and female are quite well aligned during syngamy.
While conflict between mother and her alternative chromosomes ensues, 
	fertilizing sperm decidedly side with mom, as both have a shared interest in producing a viable and potentially fit offspring. 
Our model does not directly speak to the evolutionary origin of
  female meiotic arrest \citep[for a review and evaluation of such
  hypotheses see][]{Mira1998}, in fact, we presuppose its existence.
However, given the existence of female meiotic arrest, 
	and that its timing and mechanistic details are variable
        across species \citep[Figure \ref{Meiotic_fig}, and] []{Masui_book,Karrbook:09}
	the nature of the meiotic arrest and interactions between
        sperm and egg may  be molded by selection to reduce the opportunity for female meiotic drive, 
	and counteracted by selfish drivers evolving to overcome these adaptations.

@@

\subsubsection*{Model 4. Drive-modifier in coupling phase:}
When the $C$ allele is tightly linked to the driver allele, 
	genotypic fitnesses equal $w_{AC}=w_{AB}=1-s_h$, and $w_{BC}=w_{CC}=w_{BB}=1-s$. 
Assuming HWE, a recessive fitness cost to drive, and assuming that the $A/B$ locus is at its equilibrium frequency, the change in frequency of a rare drive modifier is
\begin{equation}
	\Delta C\approx -\epsilon f_C \frac{ 1-2 d_0 (-2 d_0+s+2)+\sqrt{2} \sqrt{s (2 d_0 (d_0(s-2)+2)-1)}}{2 \bar{w}(1-2 d_0)^2}
	\label{coupling}
\end{equation}
%YB Considered this ugly math more impressive.
For all parameters sustaining a polymorphism at the drive locus ($s>d_0-1/2$), this corresponds to a decrease in frequency of the $C$ allele when it enhances drive ($\epsilon >0$ -- the $B^+$ model, above), 
	and an increase in frequency of the $C$ allele when it suppresses drive ($\epsilon <0$ -- the $B^-$ model, above). 
More generally, even when the cost of drive is not fully recessive, the $B^-$ allele will invade and fix under all parameters sustaining a previous polymorphism at the drive locus (see File S2).

\subsubsection*{Model 5. Drive-modifier in repulsion phase:}
When the $C$ allele is tightly linked to the non-driver, 
	genotypic fitnesses equal $w_{CC}=w_{AC}=w_{AA}=1$, and $w_{BC}=w_{AB}=1-s_h$. 
Assuming HWE, a recessive fitness cost to drive, and assuming that the $A/B$ locus is at its equilibrium frequency, the change in frequency of a rare drive modifier is
\begin{equation}
	\Delta C \approx -\epsilon f_{C^-}^2 \frac{ \left(2 d_0 s-\sqrt{2} \sqrt{s (2 d_0 (d_0 (s-2)+2)-1)}\right)}{2\bar{w}s (2 d_0 -1) }. \label{A-}
\end{equation}
For all values of interest ($0<s<1$, $0.5<d_0<1$), the change in frequency a rare $C$ allele is positive when it decreases drive (i.e. $\epsilon <0$, corresponding to the $A^-$ model, above), a result which holds qualitatively for a common $C$ allele, as well (File S2). 
%Somewhat counterintuitively, the spread of the $A^-$ allele is somewhat slower than that of the $B^-$ allele (it is on the order of $C^{2}$ rather than $C$). 
%This is because the $A^-$ allele will never occur in drive-homozygotes and therefore only spreads by preventing itself from the cheating of the driver.
% YB COMMENT {I removed bc this was actually quite a minor influence}

@@

{\bf{File S1:}} Transmission rules. We detail the frequency of offspring genotypes produced by each possible mating for Models 1-6 in the tabs of this Excel spreadsheet. 
\\ \\
{\bf{Files S2A \& S2B:}} A Mathematica file (FileS2A) and a PDF of this file (File S2B) in which we derive analytical results for models 1-6 and $6^\prime$. 
\\ \\
{\bf{File S3:}} Exact approach. The R Script used for exact recursions for all models, including cases with inbreeding.
\\ \\
{\bf{File S4:}} Variation in critical time-points during female meiosis across taxa (adapted from \citet{Masui_book}).
\\ \\
{\bf{File S5:}} An R object containing the phylogeny and raw data used to generate Figure \ref{Meiotic_fig}.
\\ \\
{\bf{File S6:}} The R Script used to generate Figure \ref{Meiotic_fig}. This requires that File S5 is loaded into the R environment.
\clearpage

@@

\begin{figure}
%\includegraphics[width = \textwidth]{supp/meiotic_phylogeny.pdf}
\caption{The phylogenetic distribution of the female meiotic
  arrest. The first two columns of symbols gives the stage of the ooycte when
  the sperm penetrates and the stage at which it arrests if
  unfertilized. The third column of symbols shows the site for natural fertilization. 
  These columns of phenotypic data were extracted from Table
  1 of \citet{Masui_book}. The tree was extracted from the Open Tree of
Life project. The raw data table, the phylogeny/supporting R objects, and the script to do this is are included in
the supplement (Files S4-S6). }  
\label{Meiotic_fig}
\end{figure}

@@

\begin{figure}
%\includegraphics[width = 0.8 \textwidth]{../Figures/bistable_x_vs_d_additive_s.eps} 
\caption{Evolution of a self-promoter and standard driver with variable levels of inbreeding (modifying the selfing rate from 0 to 0.9, in 0.1 increments). 
	 	Assuming that the fitnesses of drive homozygotes and 
		heterozygotes are $1-s$ and $1$, respectively. 
	 	Boundary conditions for the invasion (solid lines) 
		and fixation (dotted lines) of self-promoting (red) and standard (black) meiotic drivers, 
		with drive coefficient, $d$. 
		We derived these conditions from the simulation in File S3.}
		\label{self}
\end{figure}
